---
title: "ch5"
author: "kimsungguen"
date: "2015년 12월 5일"
output: 
  html_document: 
    keep_md: yes
---

## 5. Comparing Groups: Tables and Visualizations
### 5.1 Simulating Consumer Segment Data
  - 마케팅 분석은 종종 그룹간의 차이점을 분석함
  - 소비자의 세그먼트 데이터로 비교를해볼것이다.
  - 생성할 데이터 원본(케이블 방송 가입자 데이터와 유사)

```{r}
seg.df <- read.csv("http://goo.gl/qw303p")
```

```{r}
summary(seg.df)
```


```{r}
head(seg.df)
```

```{r}
str(seg.df)
```


  - 데이터 구조 정의(변수, 데이터 타입 등)
  - 변수의 분포를 결정하는 모수 설정 (평균, 편차 등)
  - 전체 데이터를 랜덤하게 채워넣는 반복코드 사용(for 문)

```{r}
segVars <- c("age","gender","income","kids","ownHome","subscribe") #데이터 변수
segVarType <- c("norm","binom","norm","pois","binom","binom") #변수생성 확률분포
segNames <- c("Suburb mix","Urban hip","Travelers","Moving up") #세그먼트
segSize <- c(100,50,80,70)   #세그먼트별 data 크기

#세그먼트별 각 변인의 평균(나이,성별,수익) , 이산확률(성별,자가,회원), 포아송람다(자녀)
segMeans <- matrix( c(    
  40, 0.5, 55000, 2, 0.5, 0.1,
  24, 0.7, 21000, 1, 0.2, 0.2,
  58, 0.5, 64000, 0, 0.7, 0.05,
  36, 0.3, 52000, 2, 0.3, 0.2   ), ncol=length(segVars), byrow=TRUE)

segMeans
```

```{r}
#세그먼트별 각 변인의 표준편차(나이, 수입)
segSDs <- matrix ( c(
  5, NA, 12000, NA, NA, NA,
  2, NA, 5000, NA, NA, NA,
  8, NA, 21000, NA, NA, NA,
  4, NA, 10000, NA, NA, NA ), ncol=length(segVars), byrow=TRUE)

segSDs
```

  - for문, if~else문 활용하여 데이터 생성
```{r}
seg.df <- NULL
set.seed(02554)
for (i in seq_along(segNames)) { 
 cat(i, segNames[i], "\n")

 this.seg <- data.frame(matrix(NA, nrow = segSize[i], ncol=length(segVars)))
 for (j in seq_along(segVars)) {
  if (segVarType[j] == "norm") {
    this.seg[,j] <- rnorm(segSize[i], mean=segMeans[i,j], sd=segSDs[i,j])
  } else if (segVarType[j] == "pois") {
    this.seg[,j] <- rpois(segSize[i], lambda=segMeans[i,j])
  } else if (segVarType[j] == "binom") {
    this.seg[,j] <- rbinom(segSize[i], size=1, prob=segMeans[i,j])
  } else {
    stop("Bad segment data type: ", segVarType[i])
  }
 }
 seg.df <- rbind(seg.df, this.seg)
}
```

  - 변인 이름 추가
```{r}
head(seg.df)
```

```{r}
names(seg.df) <- segVars
head(seg.df)
```


  - 세그먼트 변수 추가하고, 명목형 변수 처리

```{r}
seg.df$Segment <- factor(rep(segNames, times=segSize))
head(seg.df)
```
  
  - 이산형 데이터 라벨부여(자가, 성별, 구독여부)
```{r}
seg.df$ownHome <- factor(seg.df$ownHome, labels=c("ownNo","ownYes"))
seg.df$gender  <- factor(seg.df$gender, labels=c("Female", "Male"))
seg.df$subscribe <- factor(seg.df$subscribe, labels=c("subNo", "subYes"))
```

  - 최종데이터
```{r}
head(seg.df)
```


### 5.2 Finding Descriptives by Group
  - 특정 세그먼트 데이터 및 통계량 확인

```{r}
head(seg.df$incom[seg.df$Segment == "Moving up"])
seg.df$incom[seg.df$Segment == "Moving up"]
mean(seg.df$income[seg.df$Segment == "Moving up"])
mean(seg.df$income[seg.df$Segment == "Moving up" & seg.df$subscribe == "subNo"])
```
  - by 함수 사용하여 특정 변수기준으로 통계량 확인

```{r}
by(seg.df$income, seg.df$Segment, mean)
by(seg.df$income, list(seg.df$Segment, seg.df$subscribe), mean)

```


  - aggregate 함수 사용하여 특정 변수기준으로 통계량 확인
```{r}
aggregate(seg.df$income, list(seg.df$Segment), mean)
```

```{r}
seg.income.mean <- aggregate(seg.df$income, list(seg.df$Segment), mean)
seg.income.mean
```

  - car 패키지 some 함수로 데이터 확인
```{r}
library(car)
some(seg.df)
```

### 5.2.1 Language Brief: Basic Formula Syntax
  - 포뮬러 사용, Multiple variable formula

```{r}
#aggregate(seg.df$income, list(seg.df$Segment), mean) 같은 
aggregate(income ~ Segment, data=seg.df, mean)
```

```{r}
aggregate(income ~ Segment + ownHome, data = seg.df, mean)
```

```{r}
aggregate(income ~ Segment + ownHome + subscribe, data = seg.df, mean)
```

```{r}
agg.data <- aggregate(income ~ Segment + ownHome, data = seg.df, mean)
agg.data
```

```{r}
agg.data[2,]
agg.data[2,3]
```

  - compute frequencies using table(factor1, factor2, …)
```{r}
with(seg.df, table(Segment, ownHome))
with(seg.df, table(kids, Segment))
```

  - xtabs(formula, data) works with counts to find their total
```{r}
xtabs(kids ~ Segment, data = seg.df)
aggregate(kids ~ Segment, data=seg.df, sum)
```

```{r}
seg.tab <- with(seg.df, table(kids, Segment))
apply(seg.tab*0:7, 2, sum)
```
```{r}
seg.tab <- with(seg.df, table(kids, Segment))
colSums(seg.tab*0:7)
```

###5.2.3 Visualization by Group: Frequencies and Proportions

```{r}
require(lattice)
```

```{r}
histogram(~subscribe | Segment, data = seg.df)
```

```{r}
colSums(seg.tab*0:7)
```

```{r}
histogram(~subscribe | Segment, data = seg.df, type="count", 
          layout=c(4,1), col=c("burlywood", "darkolivegreen"))
```

```{r}
histogram(~subscribe | Segment + ownHome, data=seg.df)
```
```{r}
prop.table(table(seg.df$subscribe, seg.df$Segment), margin=2)          
```

```{r}
barchart(prop.table(table(seg.df$subscribe, seg.df$Segment), margin=2)[2,],
         xlab="Subscriber proportion by Segment", col = "darkolivegreen")
```         
### 5.2.4 Visualization by Group: Continuous Data

```{r}
seg.mean <- aggregate(income ~ Segment, data=seg.df, mean)
library(lattice)
barchart(income~Segment, data = seg.mean, col="grey")
```

```{r}
seg.income.agg <- aggregate(income ~ Segment + ownHome, data = seg.df, mean)
barchart(income ~ Segment, data=seg.income.agg,
         groups=ownHome, auto.key=TRUE,
         par.setting = simpleTheme(col=terrain.colors(2)))
```

```{r}
boxplot(income ~ Segment, data=seg.df, yaxt="n", ylab="Income ($k)")
ax.seq <- seq(from = 0, to = 120000, by=20000)
axis(side=2, at=ax.seq, labels=paste(ax.seq/1000, "k", sep=""), las=1)
```

```{r}
bwplot(Segment ~ income, data=seg.df, horizontal=TRUE, xlab="Income")
```

```{r}
bwplot(Segment ~ income | ownHome, data=seg.df, horizontal=TRUE, xlab="Income")
```

### Key point
  - writing for() loops, use seq along() instead of 1:length()
  - if() and for() blocks, always use brackets (“{” and “}”)
  - When creating a data object, pre-populate it with missing data (NA) and then fill it in
  - by() command can split up data and automatically apply functions such as mean() and summary()
  - aggregate() is even more powerful: it understands formula models and produces
  - Frequency of occurrence can be found with table()/ xtabs() is useful
  - Plots for continuous data by factor may use barchart(), or even better, boxand-whiskers plots with boxplot().
  - bwplot() command a reusable, indexable object with its results