---
title: "consumer_ch3"
author: "ksg"
date: "2015년 7월 24일"
output: 
  html_document: 
    keep_md: yes
---
### 3.1 Simulating Data
```{r}
store.df <- read.csv("http://goo.gl/QPDdMl")
head(store.df,5)
```

```{r}
k.stores <- 20 # 20 stores, using "k." for "constant"
k.weeks <- 104 # 2 years of data each
```

  - create a data frame of initially missing values to hold the data
```{r}
store.df <- data.frame(matrix(NA, ncol=10, nrow=k.stores*k.weeks))
head(store.df)

names(store.df) <- c("storeNum", "Year", "Week", "p1sales", "p2sales",
                     "p1price", "p2price", "p1prom", "p2prom", "country")
head(store.df)
dim(store.df)
```

```{r}
store.num <- 101:(100+k.stores)
store.cty <- c(rep("US", 3), rep("DE", 5), rep("GB", 3), rep("BR", 2),
               rep("JP", 4), rep("AU", 1), rep("CN", 2))

length(store.cty) # make sure the country list is the right length
head(store.df,5)
```


```{r}
store.df$storeNum <- rep(store.num, each=k.weeks)
store.df$country <- rep(store.cty, each=k.weeks)
head(store.df,5)
rm(store.num, store.cty) # clean up

store.df$Week <- rep(1:52, times=k.stores*2)
store.df$Year <- rep(rep(1:2, each=k.weeks/2), times=k.stores)
head(store.df,5)
str(store.df)
```

```{r}
store.df$storeNum <- factor(store.df$storeNum)
store.df$country <- factor(store.df$country)
str(store.df)
head(store.df) # defaults to 6 rows
```

```{r}
head(store.df, 120) # 120 rows is enough to check 2 stores; not shown
tail(store.df, 120) # make sure end looks OK too; not shown

set.seed(98250) # a favorite US postal code
store.df$p1prom <- rbinom(n=nrow(store.df), size=1, p=0.1) # 10% promoted
store.df$p2prom <- rbinom(n=nrow(store.df), size=1, p=0.15) # 15% promoted
head(store.df) # how does it look so far? (not shown)
```


```{r}
store.df$p1price <- sample(x=c(2.19, 2.29, 2.49, 2.79, 2.99),
                           size=nrow(store.df), replace=TRUE)
store.df$p2price <- sample(x=c(2.29, 2.49, 2.59, 2.99, 3.19),
                             size=nrow(store.df), replace=TRUE)
head(store.df) # now how does it look?
```

```{r}
# sales data, using poisson (counts) distribution, rpois()
# first, the default sales in the absence of promotion
tmp.sales1 <- rpois(nrow(store.df), lambda=120)
tmp.sales2 <- rpois(nrow(store.df), lambda=100)

# scale sales according to the ratio of log(price)
tmp.sales1 <- tmp.sales1 * log(store.df$p2price) / log(store.df$p1price)
tmp.sales2 <- tmp.sales2 * log(store.df$p1price) / log(store.df$p2price)

# final sales get a 30% or 40% lift when promoted
store.df$p1sales <- floor(tmp.sales1 * (1 + store.df$p1prom*0.3))
store.df$p2sales <- floor(tmp.sales2 * (1 + store.df$p2prom*0.4))
head(store.df)
```

```{r}
#install.packages("car") # if needed
library(car)
some(store.df, 10) #데이터프레임이나 매트릭스에 일부데이터를 랜덤으로 출력
```



###3.2 Functions to Summarize a Variable

  - Discrete Variables
```{r}
table(store.df$p1price)

p1.table <- table(store.df$p1price)
p1.table
str(p1.table)
plot(p1.table)
```

```{r}
table(store.df$p1price, store.df$p1prom)
p1.table2 <- table(store.df$p1price, store.df$p1prom)
p1.table2[, 2] / (p1.table2[, 1] + p1.table2[, 2])
```


  - Continuous Variables
```{r}
min(store.df$p1sales)
max(store.df$p2sales)
mean(store.df$p1prom)
median(store.df$p2sales)
var(store.df$p1sales)
sd(store.df$p1sales)
IQR(store.df$p1sales)
mad(store.df$p1sales)
```


  - central 90% of data


```{r}
quantile(store.df$p1sales, probs=c(0.05, 0.95))
quantile(store.df$p1sales, probs=0:10/10)

mysummary.df <- data.frame(matrix(NA, nrow=2, ncol=2))
names(mysummary.df) <- c("Median Sales", "IQR")
rownames(mysummary.df) <- c("Product 1", "Product 2")
mysummary.df
```




```{r}
mysummary.df["Product 1", "Median Sales"] <- median(store.df$p1sales)
mysummary.df["Product 2", "Median Sales"] <- median(store.df$p2sales)
mysummary.df["Product 1", "IQR"] <- IQR(store.df$p1sales)
mysummary.df["Product 2", "IQR"] <- IQR(store.df$p2sales)
mysummary.df
```


### 3.3 Summarizing Data Frames
```{r}
summary(store.df)
summary(store.df$Year)
summary(store.df, digits=2)
```


```{r}
#install.packages("psych")
?psych
library(psych)

#describe : Basic descriptive statistics useful for psychometrics
describe(store.df)
describe(store.df[ , c(2, 4:9)])
```

```{r}
#컬럼별 평균, 표준편차, 합계, 평균-중앙값
apply(store.df[,2:9], MARGIN=2, FUN=mean)
#apply(store.df[,2:9], 1, mean)
apply(store.df[,2:9], 2, sum)
apply(store.df[,2:9], 2, sd)
apply(store.df[,2:9], 2, function(x) { mean(x) - median(x) } )
```

```{r}
mysummary2.df <- data.frame(matrix(NA, nrow=2, ncol=2))
names(mysummary2.df) <- c("Median Sales", "IQR")
rownames(mysummary2.df) <- names(store.df)[4:5] # names from the data frame
mysummary2.df
```

```{r}
mysummary2.df[, "Median Sales"] <- apply(store.df[, 4:5], 2, median)
mysummary2.df[, "IQR"] <- apply(store.df[, 4:5], 2, IQR)
mysummary2.df
```

  - 1) CSV파일을 불러와라
  - 2) 데이터 프레임으로 변경하고 변수설정을 해라
  - 3) 데이터의 크기(차원)을 확인해라
  - 4) head 함수와 tail함수로 자료들을 확인해라(빈칸, 결측)
  - 5) some함수로 임의의 row를 확인해라
  - 6) str함수로 데이터 프레임의 구조와 변수들의 타입이 정확한지 확인하고, 변수타입을 바꿔야할 경우 바꿔라
  - 7) summary함수로 예측못한 값들을 확인해라, 특히 최대값 최소값(이산치)을 확인해라
  - 8) psych라이브러리를 활용해 데이터들의 기술통계치를 확인해라(평균, 왜도 등)


###3.4 Single Variable Visualization

```{r}
hist(store.df$p1sales)
```

```{r}
hist(store.df$p1sales,
     main="Product 1 Weekly Sales Frequencies, All Stores",
     xlab="Product 1 Sales (Units)",
     ylab="Count" )
```

```{r}
hist(store.df$p1sales,
     main="Product 1 Weekly Sales Frequencies, All Stores",
     xlab="Product 1 Sales (Units)",
     ylab="Count",
     breaks=30, # more columns
     col="lightblue")
```

```{r}
hist(store.df$p1sales,
     main="Product 1 Weekly Sales Frequencies, All Stores",
     xlab="Product 1 Sales (Units)",
     ylab="Relative frequency",
     breaks=30,
     col="lightblue",
     freq=FALSE, # freq=FALSE means plot density, not counts
     xaxt="n")

axis(side=1, at=seq(60, 300, by=20)) # add "60", "80", ...

lines(density(store.df$p1sales, bw=10), # "bw= ..." adjusts the smoothing
      type="l", col="darkred", lwd=2)
```

```{r}
boxplot(store.df$p2sales, xlab="Weekly sales", ylab="P2",
        main="Weekly sales of P2, All stores", horizontal=TRUE)
```

```{r}
boxplot(p2sales ~ p2prom, data=store.df, horizontal=TRUE, yaxt="n",
        ylab="P2 promoted in store?", xlab="Weekly sales",
        main="Weekly sales of P2 with and without promotion")

axis(side=2, at=c(1,2), labels=c("No", "Yes"))
```

```{r}
qqnorm(store.df$p1sales)
qqline(store.df$p1sales)
```

```{r}
qqnorm(log(store.df$p1sales))
qqline(log(store.df$p1sales))
```


  - my.object <- FUNCTION(my.data) # not real code
  - plot(my.object)
  - plot(FUNCTION(my.data)) 위에 두줄을 한줄로 표현한 예시

  - ecdf : empirical cumulative distribution function
  - 약자로 경험적 누적분포함수라고 해석되는데 쉽게 이해하자면 측정된 sample data를 X축을 data의 최소-최대값으로 범위를 두고 Y축을 0%에서 100%까지 누적해서 빈도를 count했을때 나타나는 함수

```{r}
plot(ecdf(store.df$p1sales),
     main="Cumulative distribution of P1 Weekly Sales",
     ylab="Cumulative Proportion",
     xlab=c("P1 weekly sales, all stores", "90% of weeks sold <= 171 units"),
     yaxt="n")

axis(side=2, at=seq(0, 1, by=0.1), las=1,
    labels=paste(seq(0,100,by=10), "%", sep=""))

abline(h=0.9, lty=3) # "h=" for horizontal line; "lty=3" for dotted
abline(v=quantile(store.df$p1sales, pr=0.9), lty=3) # "v=" for vertical line
```

```{r}
by(store.df$p1sales, store.df$storeNum, mean)
by(store.df$p1sales, list(store.df$storeNum, store.df$Year), mean)
```

```{r}
aggregate(store.df$p1sales, by=list(country=store.df$country), sum)
```

```{r}
p1sales.sum <- aggregate(store.df$p1sales,by=list(country=store.df$country), sum)
p1sales.sum
```

```{r}
#install.packages(c("rworldmap", "RColorBrewer")) # if needed
library(rworldmap)
library(RColorBrewer)

p1sales.map <- joinCountryData2Map(p1sales.sum, joinCode = "ISO2",
                                   nameJoinColumn = "country")

mapCountryData(p1sales.map, nameColumnToPlot="x",
               mapTitle="Total P1 sales by Country",
               colourPalette=brewer.pal(7, "Greens"),
               catMethod="fixedWidth", addLegend=FALSE)
```

